---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MOR

<!-- badges: start -->
<!-- badges: end -->

The goal of `MOR` is to provides post-estimation function to calculate the Median Odds Ratio
(MOR) from a multilevel binary logistic regression model fit. Currently this package
provides the median odds ratio in case of two-level random intercept model and three-level random intercept model only where the model is fitted using the R packages [`GLMMadaptive`](https://drizopoulos.github.io/GLMMadaptive/index.html) or [`glmmTMB`](https://glmmtmb.github.io/glmmTMB/).

## Installation

You can install the development version of MOR from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("shafayetShafee/MOR")
```

## Example

```{r example}
library(MOR)

data("mlm_data1", package = "MOR")
data("mlm_data2", package = "MOR")

# fitting two level random intercept model using GLMMadaptive package
model1 <- GLMMadaptive::mixed_model(fixed = Yij ~ X1c + X2b,
                              random =  ~ 1 | cluster,
                              family = binomial("logit"), data = mlm_data1)
mor(model1)

# fitting two level random intercept model using glmmTMB package
model2 <- glmmTMB::glmmTMB(Yij ~ X1c + X2b + (1 | cluster),
                      family = binomial("logit"), data = mlm_data1)

mor(model2)

# fitting three level random intercept model using glmmTMB package
model3 = glmmTMB::glmmTMB(Yijk ~ X1c + X2b + (1 | ea) + (1 | ea:hh),
                     family = "binomial", data = mlm_data2)

mor(model3)

# or
model4 = glmmTMB::glmmTMB(Yijk ~ X1c + X2b + (1 | ea/hh),
                          family = "binomial", data = mlm_data2)


mor(model4)
```

